%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.3 (29/10/16)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com) with modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%	Preamble
%------------

\documentclass[11pt,a4paper,sans]{moderncv}
\usepackage{changepage}
\usepackage{setspace}
\usepackage[total={170mm,257mm}, left=20mm, right=20mm]{geometry}
\usepackage{fontspec}
\usepackage{avant}
\usepackage{mathptmx}
\usepackage{microtype}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\moderncvstyle{casual}
\moderncvcolor{purple}

\firstname{Ágata}
\familyname{Ordano}
\title{Resumé}
\email{agata@choccymilk.dev}
\phone{+54 381 651-5378}

\begin{document}

\setromanfont{HelveticaNeueLTCom-LtCn}
\setsansfont[
	BoldFont={HelveticaNeueLTCom-BdCn}
]{HelveticaNeueLTCom-LtCn}
\setmonofont{Fira Code}


%	Title
%----------

\hfill \\[-2em]
\makecvtitle % Print the CV title
\hfill \\[-6em]

%	About Me
%-------------

\section{About Me}

 { \flushleft As a software developer with \textbf{4+ years} of experience, I specialize in \textbf{Full Stack} Web Development and \textbf{Cloud Infrastructure}, including platforms like GCP and AWS. My proficiency extends to Sysadmin and DevOps, especially in small organizational environments. \\ I'm adept in \textbf{TypeScript} and \textbf{Rust} and have a versatile background in languages such as \textbf{PHP}, \textbf{Python}, \textbf{JavaScript}, and technologies like \textbf{CakePHP}, \textbf{React}, \textbf{Svelte} and \textbf{Firebase} and databases including \textbf{MySQL}, and some \textbf{NoSQL} systems. My quick adaptability is complemented by my diverse background in Graphic Design, Engineering, UX, and business development, enriching my approach to software solutions and multidisciplinary teamwork. 

 }

%	Work
%------------


\section{Work Experience}
{\setstretch{0.7}
\cventry{2022 - Present}{Infra and Full Stack Developer}{BidBit}{}{}{}
{
	
\begin{itemize}
	\item Spearheaded the modernization of a legacy PHP system, transitioning to a new architecture on GCP for improved scalability and reliability.
	\item Implemented TypeScript in refactoring legacy frontend code, aligning with modern development practices.
	\item Integrated CI/CD into production, using a custom Rust-based pipeline.
	\item Developed several new backend features, incorporating Object Storage, logging, tracing, caching, authorization, and more.
	\item Performed webmaster activities including domain management, mailing, and monitoring.
\end{itemize}
 } \hfill \\[-1em]
\hfill \\

\cventry{2019 - 2022}{Software Developer}{Environmental Hub Foundation}{}{}{}
{
\begin{itemize}
	\item Managed various projects including website development and internal tool creation.
	\item Worked predominantly with TypeScript, Rust, and Python.
	\item Balanced roles in sysadmin, cloud management (AWS/hybrid), software development, and technical writing.
\end{itemize}	
} \hfill \\[-1em]
\hfill \\

\cventry{2018 - 2019}{Web Developer}{Freelance}{}{}{}
{
	\begin{itemize}
		\item Specialized in Jamstack-based frontend development using React, Angular, and Vanilla JS/TS.
		\item Undertook CSS-intensive and design-centric projects.
		\item Engaged in backend development with PHP, NodeJS, and Python.
	\end{itemize}	
} \hfill \\[-1.5em]
\hfill \\


%	Education
%------------


\section{Education}
\cventry{2016 onwards}{Self Taught}{}{}{}{}
{
	\begin{itemize}
		\item Actively engaged in self-directed learning for an extended period to develop software development skills.
		\item Expanded knowledge in complementary fields like Business Management, Design, UX, Psychology, Marketing, Economics, and Mathematics to generate business acumen.
	\end{itemize}	
}
\hfill \\[-0.5em] 

\cventry{2009 - 2016}{Mechanical Electrical Technician}{UNT Technical Institute}{}{}{}
{
	\begin{itemize}
		\item Completed a program equivalent to an Associate Degree.
		\item Acquired foundational technical and engineering skills in mechanical and electrical systems, including design and execution of electromechanical devices and installations in the industry.
	\end{itemize}	
	%\flushleft Competencies include: \begin{itemize}
	%	\item Design, installation and mainteinance of electrical machinery in low and mid voltage, fixed and mobile structures, and hydraulic/pneumatic systems.
	%	\item Programming and installation of industrial PLCs and smart relays.
	%	\item Design and management of small-scale industrial plants.
	%	\item Thesis accesible at \href{https://goo.gl/JtjfTV}{\color{blue}{goo.gl/JtjfTV}}.
	%\end{itemize}
}
\hfill \\[-0.5em]

%	Extras
%------------

\section{More Stuff}

\cvitemwithcomment{}{GitHub}{\flushleft \href{https://github.com/aordano}{\color{blue}{github.com/aordano}}}
\cvitemwithcomment{}{LinkedIn}{\flushleft \href{https://www.linkedin.com/in/ordanoagata/}{\color{blue}{linkedin.com/in/ordanoagata}}}
%\cvitemwithcomment{}{Portfolio}{\flushleft \href{https://pf.choccymilk.dev}{\color{blue}{pf.choccymilk.dev}}}  %[WIP]
%\cvitemwithcomment{}{Blog}{\flushleft \href{https://blog.choccymilk.dev}{\color{blue}{blog.choccymilk.dev}}}  %[WIP]
\cvitemwithcomment{}{Recursion}{\flushleft \href{https://cv.choccymilk.dev/cv.pdf}{\color{blue}{cv.choccymilk.dev}}}
%\cvitemwithcomment{}{Cat pics}{\flushleft \href{https://cats.choccymilk.dev}{\color{blue}{cats.choccymilk.dev}}}  %[WIP]
\hfill \\

Check out the source for this CV at \href{https://github.com/aordano/cv}{\color{blue}{github.com/aordano/cv}}.

\end{document}